%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Research}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Ongoing research}
{EPFL, DCSL}
{Lausanne, Switzerland}
{Aug. 2017 - Present}
{
	\begin{cvitems}
	\item{Modern system-oriented programming languages, software security, integrity, and confidentiality in Cloud deployments, Intel SGX}
	\end{cvitems}
}


\cventry
{Light-weight contexts in Dune}
{EPFL, DSCL}
{Lausanne, Switzerland}
{Sep. 2016 - Jul. 2017}
{
	\begin{cvitems}
	\item{Allow processes to create and switch among different address spaces in a virtualized environment and experimented with loading/copying optimizations yielding a 5x improvement over fork.}
	\item{Intel VTX, Dune, Virtualization, Kernel module, Virtual Memory Management}
	\end{cvitems}
}

\cventry
{Efficient runtime Deoptimization for R(Master Thesis)} % Job title
{Northeastern University} % Organization
{Boston, U.S.A.} % Location
{Sep. 2015 - Mar. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Implemented an assumption-based optimizer for an R JIT compiler to remove performance bottlenecks inherent to the language, while preserving semantics at runtime.}
\item {On-stack replacement, assumption-based compiler optimizations, runtime deoptimization, R, LLVM, JIT compilers}
\end{cvitems}
}

\cventry
{Aperiodic Support in FASA}
{ABB Corporate Research}
{Baden, Switzerland}
{Feb. 2015 - Aug. 2015}
{
	\begin{cvitems}
	\item{Supervised by Dr. Manuel Oriol}
	\item{Fixed-priority servers, data-driven events, real-time control applications, kernel design, dynamic linking/loading \& software updates, pi-calculus}
	\end{cvitems}
}

\cventry
{Scalameta: AST Persistence \& Obey: Code Health}
{EPFL, LAMP}
{Lausanne, Switzerland}
{Jan. 2014 - Feb. 2015}
{
	\begin{cvitems}
	\item{Supervised by Prof. Martin Odersky \& Dr. Eugene Burmako}
	\item{Obey: Scala compiler plugin that allows to automatically correct \& reformat scala source code at compile time to enforce user-defined rules, adapt to library API changes, or comply with a different Scala compiler.}
	\item{AST Persistence: Designed \& implemented a new format to store compressed typed abstract syntax trees along scala binaries to resolve compiler version incompatibilities and code/maccros expansion in IDEs.}
	\end{cvitems}
}



\end{cventries}